Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-21 R0V0.tex
Changes on the proof of Theorem 2, regarding the minimization of the energy instead of the minimization of the length

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the length of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		\ell(\varphi)=\int_0^1\sqrt{\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)}\,ds\;.
	\end{equation}

	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. More precisely, 
	\begin{equation*}
		\gamma=\arg\inf\ell(\varphi)\Leftrightarrow\gamma_i=\arg\inf e(\varphi_i),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
	\end{equation*}
	Consequently, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.

>>>>

	It remains to integrate $\delta_k$ to obtain a feedback law for system \eqref{eq:general system} satisfying the constraints of Problem \ref{problem formulation}. Because $M$ is a block-diagonal matrix, the energy of any curve $\varphi:[0,1]\to\mathbb{R}^n$ satisfies the following equation
	\begin{equation}\label{eq:geodesic sum}
		e(\varphi)=\int_0^1\sum_{i=1}^N V_i\left(\varphi_i(s_i),\tfrac{\partial \varphi_i}{\partial s_i}(s_i)\right)\,ds\;.
	\end{equation}

	Since $M$ is positive definite, the minimum of Equation \eqref{eq:geodesic sum} corresponds to a minimum of each component $i\in\mathbb{N}_{[1,N]}$. Moreover, for a geodesic curve $\gamma$, $e(\gamma)=\ell(\gamma)$. Consequently,
	\begin{equation*}
		\gamma_i=\arg\inf e(\varphi_i)\Leftrightarrow\gamma=\arg\inf\ell(\varphi),\quad\forall i\in\mathbb{N}_{[1,N]}\;.
	\end{equation*}
	Thus, the minimization of Equation~\eqref{eq:geodesic sum} can be computed in parallel.
